Initial Analysis

### 2019-09-12 Initial_Analysis.Rmd
Updated main function to account for "discrete" stocks. Still need to modify path to new folder

#### RFMO

```{r RFMO_Index, eval = F, echo = F}

# SAU RFMO shapefile

# The path
path_world <- paste(Data_Path,"Spatial_Data/RFMO/SAU_RFMO",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  dplyr::rename(Name = RFMO_nm_s) %>% 
  st_set_crs(3832) %>% # Making sure is same proyection
  st_transform(3832) # to match shapefiles

# Load coordinate system

Coor <- fread(paste(Data_Path,"Spatial_Data/Lon_Lat_DBEM.txt",sep=""),header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# COnvert Coor system to sf
Coor_sf = st_as_sf(Coor,
                        coords = c("Longitude", "Latitude")) %>% 
  st_set_crs(3832) %>% # to match shapefiles
  st_transform(3832) # to match shapefiles

# Merge RFMO and coor datasets
RFMO_Coor <- st_join(RFMOs_sf,
                         Coor_sf,
                         join = st_contains) %>% 
  filter(!is.na(INDEX)) # Remove regions beyond RFMOs

# head(RFMO_Coor)

# Convert it back to a data frame and select only the two columns we want
RFMO_INDEX <- as.data.frame(RFMO_Coor) %>% 
  select(INDEX,Name) %>% 
  arrange(INDEX)

# head(RFMO_INDEX)

# Save new data
write.csv(RFMO_INDEX,
          paste(Data_Path,"Spatial_Data/RFMO/RFMO_INDEX.csv",sep=""),
          row.names = F
          )

# Map it (works!)

# RFMO_INDEX %>%
#   left_join(Coor,
#             by = "INDEX") %>%
#   ggplot(.,
#             aes(x = Longitude,
#                 y = Latitude,
#                 color = Territory,
#                 fill = Territory)
#             ) +
#   geom_tile() 
# 
# 
# RFMO_INDEX %>%
#   left_join(Coor,
#             by = "INDEX") %>%
#   ggplot(.,
#             aes(x = Longitude,
#                 y = Latitude,
#                 color = INDEX,
#                 fill = INDEX)
#             ) +
#   geom_tile() +
#   facet_wrap(~Territory)

```{r RFMO_Neighbourds_Control_Pannel, eval = F, echo = F}

# SAU RFMO shapefile

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_RFMO",sep="")
# #The File
fnam_world <- "SAU_RFMO_Sept_2015.shx"
# #Load it!
# 
RFMOs_sf <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world)) %>% 
  dplyr::rename(Name = RFMO_nm_s)

# Run Function (Ran and saved May 27 2019 at 6pm)
 system.time(
  RFMO_Neighbour_List <- EstNeighbours(RFMOs_sf, Partial = T)
 )
# 8203.05    0.25 8204.51 (around 2 hours 30 min)

 ## Include Index column

RFMO_Neighbour_List <- fread(paste(Data_Path,"Spatial_Data/RFMO/RFMO_Neighbour_List.csv",sep=""),header = TRUE) %>% 
  left_join(RFMO_INDEX,
            by = "Name") %>% 
  rename(Territory = Name,
         Neighbour = Neighbour_Territory)

# head(RFMO_Neighbour_List)

write.csv(RFMO_Neighbour_List,
          paste(Data_Path,"Spatial_Data/RFMO_Neighbour_List.csv", sep =""),
          row.names = F)

@@

    # For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
    SAU_C_data <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
      select(CATCH.1:CATCH.65) %>% 
      mutate(INDEX = INDEX) %>% 
      gather("Year","Catch",1:10) %>% # Last 10 years of data
      group_by(INDEX) %>% 
      summarise(SAU_C = mean(Catch,na.rm=T))

@@

#### For testing 
# Spp <- #600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Model <- "All"
# Coord = CoorG

# For EEZ
 # Neighbours <- Neighbours_EEZ
 # Index_Code <- EEZ_Index_Code

 # For RFMO 
 # Index_Code <- RFMO_INDEX
 # Neighbours <- RFMO_Neighbor_List %>% 
 #   rename(Territory = Name,
 #         Neighbour = Neighbor_Territory)

# __________________________________
# __________________________________

@@

@@

@@

# __________________________________
# Test function
# __________________________________
# EstTransIndex(Spp = 600107,
#               Mode = "All",
#               Neighbours = ,Coord,Index_Code,Save="Y")
# 
# Spp <-  # Tuna Many RFMOs
# Model <- "All"
# Coord = CoorG
# 
# # For EEZ
#  # Neighbours <- Neighbours_EEZ
#  # Index_Code <- EEZ_Index_Code
#  
#  # For RFMO 
#  Index_Code <- RFMO_INDEX
#  Neighbours <- RFMO_Neighbor_List %>% 
#    rename(Territory = Name,
#          Neighbour = Neighbor_Territory)

@@

# Creates dummy dataset for Non transboundary species
write.csv(tibble(TaxonKey = "NA"), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)

@@

# Run model in parallel
system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List,
      FUN = EstTransIndex,
      Model = "All", # all data sources
      Neighbours = Neighbours_Data,
      Coord = CoorG,  # Gabriels coordinate system for read species dist
      Index_Code = Index_Code, 
      Save = "Y",  # For saving
      Jurisdiction_Type = Jurisdiction # For saving in proper path
    )
  )
)

@@

## Sub Routine; SAU Catch

###`getSAucat`

```{r getSAUCatch, eval = F, echo = F}

# Function to get sau Catch data and total per country over a mean of (standarized 10 years )
getSAUCatch <-function(TaxonKey, Coord, nyears = 10){
  suppressMessages(

  year <- 67-nyears-1

Catch_Data <- GetSppDist(TaxonKey,Model="SAU_C",Coord = Coord) %>% 
  select(year:67) %>% 
  gather("Year","Catch",1:nyears) %>% 
  filter(!is.na(Catch)) %>%  # remove NAs earlier
  left_join(Index_Code,
            by ="INDEX") %>% 
  group_by(Species,Territory,Year) %>% 
  summarise(Total_Catch = sum(Catch,na.rm=T)) %>% 
  group_by(Species,Territory) %>% 
  summarise(Mean_Catch = mean(Total_Catch,na.rm=T))
)
return(Catch_Data)

#### Run Subroutine

```{r SAU_Catch_Data, eval = F, echo = F}

# get SAU catch data per species per nation

# Data needed for function
CoorG <- read.csv(paste(Data_Path,"Spatial_Data/coordinates_gab.csv",sep="")) %>%
  mutate(INDEX = seq(1,259200,1))

EEZIDs_List <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/Updated_EEZList_17June2016.xlsx",sep=""))
EEZ_CellID <- read_excel(paste(Data_Path,"Spatial_Data/V_Lam/EEZ_CellID.xlsx",sep=""))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

  # Get list of species catch
Trans_Spp_List <- unique(Clean_Results_Trans$TaxonKey)

# Run routine and save it for latter
Sau_Catch_Data <- bind_rows(mclapply(Trans_Spp_List, getSAUCatch, Coord=CoorG))

write.csv(Sau_Catch_Data,
          paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep=""),
          row.names = F)

@@

  # Set the path for each file
  Distpath <- paste(Results_Path,Spp,sep="")

@@

# Updates result's path for the jurisdiction
Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")
Results_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Old_Results/"

@@

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  group_by(Territory = Country.or.Area,
    georegion = Region.Name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(Territory != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  mutate(
    Territory = gsub("\\s*\\([^\\)]+\\)","",Territory),
    Territory = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",Territory),
    Territory = gsub( "United States of America", "USA",Territory),
    Territory = gsub("Democratic People's Republic of Korea", "Korea (North)",Territory),
    Territory = gsub("Republic of Korea", "Korea (South)",Territory),
    Territory = gsub("Iran (Islamic Republic of)", "Iran",Territory),
    Territory = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",Territory),
    # Territory = gsub("Congo", "Congo, R. of",Territory),
    Territory = gsub("United Republic of Tanzania", "Tanzania",Territory),
    Territory = gsub("Cabo Verde", "Cape Verde",Territory),
    Territory = gsub("Timor-Leste", "Timor Leste",Territory),
    Territory = gsub(" and ", " & ",Territory),
    # Territory = gsub("Puerto Rico (USA)", "Puerto Rico",Territory),
    Territory = gsub("Taiwan", "Taiwan (China)",Territory)
  )

@@

# head(World_land_sf)
# Transboundary Results ####

# For Carmelia
if(Jurisdiction == "EEZ"){
  if(Sys.info()[7] == "carmelia"){
    Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep="")) # losad carmelia data
  }else{
    # Read Sau Catch Data
    Sau_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
      filter(!is.na(Territory))
    # For Hall and The Beast
    # List of species
    Spp <- list.files(Results_Path)[1:672]

    # Get resukts for all species
    Results_Trans <- GetTransResults(Spp)

    # Clean out countries that share with their own borders (Will be outdated soon)
    Auto_Remove_Territories <- Results_Trans %>%   
      rename(FishingRegion=Country_Territory) %>% 
      left_join(Clean_sau_eez_fes,
                by = "FishingRegion") %>% 
      select(TaxonKey,
             Country_Territory= FishingRegion,
             FishingRegion=Neighbor_Territory, #Neighbour_Territory
             Model_Index,
             Area_Index,
             CT_fishing_entity= fishing_entity) %>% 
      left_join(Clean_sau_eez_fes,
                by = "FishingRegion") %>% 
      select(1,2, 
             Neighbor_Territory = FishingRegion,
             Model_Index:CT_fishing_entity,
             NT_fishing_entity= fishing_entity,
             everything()) %>% 
      mutate(
        CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
        NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
        Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
      )

@@

    # List of territories to eliminate (No other neighobors but mainland)
    Islands_to_Remove <- c(
      "Brazil (Fernando de Noronha)",
      "Brazil (St Paul and St. Peter Archipelago)",
      "Hawaii Main Islands (USA)",
      "Hawaii Northwest Islands (USA)",
      "Juan Fernandez Islands (Chile)",
      "Kermadec Isl. (New Zealand)"
    )

@@

    Territories_to_Remove <- Results_Trans %>% 
      filter(
        Country_Territory %in% Islands_to_Remove |
          Neighbor_Territory %in% Islands_to_Remove |
          Country_Territory == "Balearic Island (Spain)" & Neighbor_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
          Country_Territory == "British Virgin Isl. (UK)" & Neighbor_Territory == "Anguilla" |
          Neighbor_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
          Country_Territory == "Corsica (France)" & Neighbor_Territory == "France (Mediterranean)" |
          Neighbor_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
          Country_Territory == "Crete (Greece)" & Neighbor_Territory == "Grece" |
          Neighbor_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
          Country_Territory == "Cyprus (North)" & Neighbor_Territory == "Cyprus (South)" |
          Neighbor_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
          Country_Territory == "Channel Isl. (UK)" & Neighbor_Territory == "United Kingdom" |
          Neighbor_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
          Country_Territory == "Glorieuse Islands (France)" & Neighbor_Territory == "Mayotte (France)" |
          Neighbor_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
          Country_Territory == "Guam (USA)" & Neighbor_Territory == "Northern Marianas (USA)" |
          Neighbor_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
          Country_Territory == "Italy" & Neighbor_Territory == "Sardinia (Italy)" |
          Neighbor_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
          Country_Territory == "Italy" & Neighbor_Territory == "Sicily (Italy)" |
          Neighbor_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
          Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (main islands)"|
          Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
          Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (Ogasawara Islands)"|
          Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
          Country_Territory == "Norway" & Neighbor_Territory == "Svalbard Isl. (Norway)" |
          Neighbor_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
          Country_Territory == "Sicily (Italy)" & Neighbor_Territory == "Sardinia (Italy)" |
          Neighbor_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
          Country_Territory == "South Africa (Atlantic Coast)" & Neighbor_Territory == "South Africa (Indian Ocean Coast)" |
          Neighbor_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
          Country_Territory == "USA (Alaska, Arctic)" & Neighbor_Territory == "USA (Alaska, Subarctic)" |
          Neighbor_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
      ) %>%
      group_by(Country_Territory,Neighbor_Territory) %>% 
      summarise(n())

    # Cleaned results 
    Clean_Results_Trans <- Auto_Remove_Territories %>% 
      anti_join(Territories_to_Remove,
                by = c("Country_Territory","Neighbor_Territory")
      ) %>% 
      filter(Same_Nation == "No") %>% 
      rename(Territory = Country_Territory,
             Neighbour = Neighbor_Territory)

    # The path
    path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
    # #The File
    fnam_world <- "SAUEEZ_July2015.shp"
    # #Load it!

    ### Sau Catch Data

    SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv",sep = ""), header = TRUE)

  } # closes ifstatement for carmelia temporal files
}else{ # Closes EEZ ifelse

  # List of files without the non-trans data file
  Spp <- list.files(Results_Path)
  Spp <- Spp[Spp !="Non_Transboundary_Data.csv"]

  # Results loaing 
  Results_Trans <- GetTransResults(Spp)

  # Cleaning results (No cleaning needed for now)
  Clean_Results_Trans <- Results_Trans

  # Load results for non transboundary (discrete) stocks
  Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep="")) %>% 
    filter(!is.na(TaxonKey))

  # Shapefiles 
  path_world <- paste(Data_Path,"Spatial_Data/RFMO/SAU_RFMO/",sep="")
  # #The File
  fnam_world <- "SAU_RFMO_Sept_2015.shp"

#  GLobal data depending on jursidiction
# Load Regional shapefiles 
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(Territory = Name)

@@

Transboundary_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI#,
         # Same_Nation == "No"
         ) %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
    )

@@

World_sf_si <- World_sf %>%
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=moll") %>% # tubed world
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="Territory")

Catch_Country <- Sau_Catch_Data %>% 
  group_by(FishingRegion=Territory) %>% 
  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
  filter(!(is.na(FishingRegion))) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(Total_Catch = sum(Total_Catch,na.rm=T))

World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=moll") %>% # tubed world
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
  left_join(Catch_Country, by ="Territory") # Include total specices catch

@@

unique(World_sf_si$Bins)
unique(World_sf_si_land$BinsLan)

levels(World_sf_si$Bins)
levels(World_sf_si_land$BinsLan)

Plot <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = BinsLan)) +
  geom_sf(data = World_sf_si,aes(fill = Bins)) + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
  #                              rev(wes_palette(n = 4, name = "Darjeeling1"))
  #                              ),
  #                    na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#F98400","#F98400","#F2AD00","#F2AD00","#00A08A","#FF0000","#FF0000","#FF0000"),
                     na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

Plot_Name <- paste(Jurisdiction,"_100_25_Bins_Land.png", sep = "")

@@

>>>>

@@

    # For now we're using only the last 10 years average, basicaaly if the species has been fished in any of these years, its considered present
    SAU_C_data <- as.data.frame(R.matlab::readMat(SppPath)) %>% 
      select(CATCH.1:CATCH.65) %>% 
      mutate(INDEX = INDEX) %>% 
      gather("Year","Catch",CATCH.56:CATCH.65) %>% # Last 10 years of data
      group_by(INDEX) %>% 
      summarise(SAU_C = mean(Catch,na.rm=T))

@@

#### For testing 
# Spp <- 604250  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Spp <- 600464 # Discrete species 
# x <- c(600464, # Discreat spp in one nation
      # 600059, # nowhere to be found spp
       # 601352, # Discrete spp in two nations
       # 600004) # transboundary spp
# Model <- "All"
# Coord <- CoorG
# 
# # For EEZ
# Neighbours <- Neighbours_Data
# Index_Code <- Index_Code
#  
# __________________________________
# __________________________________

@@

  # if(n_Territory > 1){

@@

  # IF SPECIES DISCRETE AND APEARS IN ONLY 1 REGION OR > 1 REGION BUT NOT NEIGHBOURS #

  if(nrow(Spp_Grid) == 0 & Save == "Y"){

    # IF SPECIES IS DISCRETE AND ONLY APEARS IN ONE REGION
  Discrete_Territory <- unique(Model_Index_D$Territory)
  n_Territory <- length(Discrete_Territory)

    # Get current Spp that is not transboundary 
    Current_Spp <- tibble(TaxonKey = as.integer(Spp),
                          Territory = Discrete_Territory)

    if(n_Territory ==1){

    To_Print <- paste(Spp, "is only present in",Discrete_Territory)
    print(To_Print)
    paste(Spp, "is only present in",Discrete_Territory)
    }else{

      To_Print <- paste(Spp, "is in both (non-neighbouring)",Discrete_Territory[1],Discrete_Territory[2])
      print(To_Print)
    }

  EstTransIndex=Current_Spp
    print(To_Print)
  }

  if(nrow(Spp_Grid) > 0 & Save == "Y"){

@@

  }
  ### Function return
  EstTransIndex=Indexes # A dataframe with

  } # Closes Treshold 3
}

# __________________________________
# Test function
# __________________________________

# Spp <-  # Tuna Many RFMOs
# Model <- "All"
# Coord = CoorG
# #
# 
# # For EEZ
# Neighbours <- Neighbours_EEZ
# Index_Code <- EEZ_Index_Code
# 
# 
# EstTransIndex(Spp = 600107,
#               Mode = "All",
#               Neighbours = ,Coord,Index_Code,Save="Y")

@@

# Creates dummy dataset for Non transboundary species
write.csv(tibble(), paste(Results_Path,"Non_Transboundary_Data.csv",sep=""), row.names = F)

@@

# Run model in parallel
system.time(
  Dis_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List,
      FUN = EstTransIndex,
      Model = "All", # all data sources
      Neighbours = Neighbours_Data,
      Coord = CoorG,  # Gabriels coordinate system for read species dist
      Index_Code = Index_Code, 
      Save = "Y",  # For saving
      Jurisdiction_Type = Jurisdiction # For saving in proper path
    )
  )
)

@@

@@

  # Set the path for each file
  Distpath <- paste(Results_Path,"/Trans_Results/",Spp,sep="")

@@

# In case you want to use old results (ran with older verion of neighbours)
# Results_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Old_Results/"

@@

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  group_by(Territory = Country.or.Area,
           georegion = Region.Name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(Territory != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    Territory = gsub("\\s*\\([^\\)]+\\)","",Territory),
    Territory = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",Territory),
    Territory = gsub( "United States of America", "USA",Territory),
    Territory = gsub("Democratic People's Republic of Korea", "Korea (North)",Territory),
    Territory = gsub("Republic of Korea", "Korea (South)",Territory),
    Territory = gsub("Iran (Islamic Republic of)", "Iran",Territory),
    Territory = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",Territory),
    # Territory = gsub("Congo", "Congo, R. of",Territory),
    Territory = gsub("United Republic of Tanzania", "Tanzania",Territory),
    Territory = gsub("Cabo Verde", "Cape Verde",Territory),
    Territory = gsub("Timor-Leste", "Timor Leste",Territory),
    Territory = gsub(" and ", " & ",Territory),
    # Territory = gsub("Puerto Rico (USA)", "Puerto Rico",Territory),
    Territory = gsub("Taiwan", "Taiwan (China)",Territory)
  )

@@

# head(World_land_sf)

# Load EEZ shapefiles 
# SAU shapefile name and paths

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile/",sep="")
# #The File

fnam_world <- "SAUEEZ_July2015.shp"
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(Territory = Name)

# ---------------------------- #
# Transboundary Results ####
# ---------------------------- #

if(Sys.info()[7] == "carmelia"){ # For Carmelia

  Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep="")) # losad carmelia data
}else{  # For Hall and The Beast

  # Read Sau Catch Data
  Sau_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
    filter(!is.na(Territory))

  # List of species
  Spp <- list.files(paste(Results_Path,"/Trans_Results",sep=""))[1:672]

  # ---------------------------- #
  # Load and clean Transboundary results
  Results_Trans <- GetTransResults(Spp)

  # Clean out countries that share with their own borders (e.g. USA gulf of Mx and East coast)
  Auto_Remove_Territories <- Results_Trans %>%   
    rename(FishingRegion=Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(TaxonKey,
           Territory= FishingRegion,
           FishingRegion=Neighbour, #Neighbour_Territory
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(1,2, 
           Neighbour = FishingRegion,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

@@

  # List of territories to eliminate (No other neighobors but mainland)

  Islands_to_Remove <- c(
    "Brazil (Fernando de Noronha)",
    "Brazil (St Paul and St. Peter Archipelago)",
    "Hawaii Main Islands (USA)",
    "Hawaii Northwest Islands (USA)",
    "Juan Fernandez Islands (Chile)",
    "Kermadec Isl. (New Zealand)"
  )

@@

  Territories_to_Remove <- Results_Trans %>% 
    filter(
      Territory %in% Islands_to_Remove |
        Neighbour %in% Islands_to_Remove |
        Territory == "Balearic Island (Spain)" & Neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
        Territory == "British Virgin Isl. (UK)" & Neighbour == "Anguilla" |
        Neighbour == "British Virgin Isl. (UK)" & Territory == "Anguilla" |
        Territory == "Corsica (France)" & Neighbour == "France (Mediterranean)" |
        Neighbour == "Corsica (France)" & Territory == "France (Mediterranean)" |
        Territory == "Crete (Greece)" & Neighbour == "Grece" |
        Neighbour == "Crete (Greece)" & Territory == "Grece" |
        Territory == "Cyprus (North)" & Neighbour == "Cyprus (South)" |
        Neighbour == "Cyprus (North)" & Territory == "Cyprus (South)" |
        Territory == "Channel Isl. (UK)" & Neighbour == "United Kingdom" |
        Neighbour == "Channel Isl. (UK)" & Territory == "United Kingdom" |
        Territory == "Glorieuse Islands (France)" & Neighbour == "Mayotte (France)" |
        Neighbour == "Glorieuse Islands (France)" & Territory == "Mayotte (France)" |
        Territory == "Guam (USA)" & Neighbour == "Northern Marianas (USA)" |
        Neighbour == "Guam (USA)" & Territory == "Northern Marianas (USA)" |
        Territory == "Italy" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Italy" & Territory == "Sardinia (Italy)" |
        Territory == "Italy" & Neighbour == "Sicily (Italy)" |
        Neighbour == "Italy" & Territory == "Sicily (Italy)" |
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (main islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (main islands)"|
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (Ogasawara Islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (Ogasawara Islands)"|
        Territory == "Norway" & Neighbour == "Svalbard Isl. (Norway)" |
        Neighbour == "Norway" & Territory == "Svalbard Isl. (Norway)" |
        Territory == "Sicily (Italy)" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Sicily (Italy)" & Territory == "Sardinia (Italy)" |
        Territory == "South Africa (Atlantic Coast)" & Neighbour == "South Africa (Indian Ocean Coast)" |
        Neighbour == "South Africa (Atlantic Coast)" & Territory == "South Africa (Indian Ocean Coast)" |
        Territory == "USA (Alaska, Arctic)" & Neighbour == "USA (Alaska, Subarctic)" |
        Neighbour == "USA (Alaska, Arctic)" & Territory == "USA (Alaska, Subarctic)"
    ) %>%
    group_by(Territory,Neighbour) %>% 
    summarise(n())

  # Cleaned results 
  Clean_Results_Trans <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9)

  # ---------------------------- #

  # Load and clean Discrete results
  Discrete_Data <- fread(paste(Results_Path,"/Trans_Results/Non_Transboundary_Data.csv",sep="")) %>% 
    left_join(Exploited_Species)

} # closes ifstatement for carmelia temporal files

@@

Transboundary_Spp <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI
         ) %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
    )

@@

World_sf_si <- World_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="Territory")

Catch_Country <- Sau_Catch_Data %>% 
  group_by(FishingRegion=Territory) %>% 
  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T)/1000000,2)) %>% 
  filter(!(is.na(FishingRegion))) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
  mutate(Territory = gsub("USA","United States of America",Territory))

World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=wintri") %>% # tubed world
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
  left_join(Catch_Country, by ="Territory") # Include total specices catch

# Get the NA's to be grey
Grey_land <- World_sf_si_land %>% 
  filter(is.na(BinsLan))

@@

# unique(World_sf_si$Bins)
# unique(World_sf_si_land$BinsLan)

# levels(World_sf_si$Bins)
# levels(World_sf_si_land$BinsLan)

Plot <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = BinsLan), colour = "grey80") +
  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20") + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = BinsLan),fill = "grey80") + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
                               rev(wes_palette(n = 5, name = "Darjeeling2"))
                               ),
                     na.value = "white"
  ) +
  # scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#F98400","#FF0000","#FF0000","#FF0000"),
  #                    na.value = "white"
  # ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

Plot_Name <- paste(Jurisdiction,"_100_25_Bins_Landb.png", sep = "")

@@

Data <- World_sf_si_land %>% 
  as_tibble() %>% 
  select(Territory, BinsLan)

Data_EEZ <- World_sf_si %>% 
  as_tibble() %>% 
  select(Territory, Bins)

### EEZ shapefile
eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks

eez = spTransform(eez, CRS("+proj=longlat"))
eez = spTransform(eez, CRS("+proj=wintri"))
eez = fortify(eez)

World_sf_si <- World_sf %>%
  st_transform(crs = 4326

#### Round map tryout 
mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))

mapworld<- mapworld %>% 
  rename(Territory = id) %>% 
  left_join(Data,
            by = "Territory") %>% 
  left_join(Data_EEZ,
            by = "Territory") %>% 
  rename(id = Territory)

# head(mapworld)

#create map boundary
ll.to.wt <- function (points)
  as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
                            CRS("+proj=wintri")))

lseq = seq(-85, 85, by=.25)
boundary <- ll.to.wt(data.frame(
  long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
  lat  = c(lseq,                    rev(lseq),          lseq[1])))
